
```{r}
library(tidyverse)
library(ggplot2)
library(GGally)
library(survey)
```

```{r}
df <- read.csv("tutorialdf.csv")
```


```{r}
head(df)
```

```{r}
# for getting target population
pop <- subset(df, subset = ((DUQ200 == 1 | DUQ200 == 2) & INQ020 == 1))

# for filtering out nulls
pop <- subset(pop, subset = IND235 <= 12)
```

```{r}
pop
```
Is there a significant difference in monthly family income between people who use and don't use marijuana?

```{r}
ggplot(pop, aes(x = IND235, fill = factor(DUQ200))) + 
  geom_bar(position =  'fill') +
  labs(title = "Distribution of Income", x = "Monthly Family Income", y = "Frequency", fill = "Ever Used Marijuana") +
  scale_fill_discrete(labels = c("Yes", "No"))
```

```{r, fig.width = 5, fig.height = 3}
ggplot(pop, aes(x = factor(DUQ200), y = IND235, fill = factor(DUQ200))) + 
  geom_boxplot(show.legend = FALSE) +
  labs(title = "Distribution of Income", x = "Ever Smoked Marijuana?", y = "Monthly Family Income", fill = "Ever Used Marijuana") +
  scale_fill_brewer(palette="Dark2") + 
  scale_x_discrete(labels = c("1" = "Yes", "2" = "No"))
```


```{r}
t.test(pop[pop$DUQ200 == 1,]$IND235, pop[pop$DUQ200 == 2,]$IND235)
```

Categorize people into low, medium, high usage of marijuana users
```{r}
mari = pop[pop$DUQ200 == 1,]

# only include those who responded to DUQ217: "During the time that you smoked marijuana or hashish, how often would you usually use it?"
mari_sub = subset(mari, subset = DUQ217 < 7)
usage <- ifelse(mari_sub$DUQ217 <= 3, "low", 
              ifelse(mari_sub$DUQ217 == 4, "medium", "high"))
mari_sub$usage = usage
mari_sub$usage <- ordered(mari_sub$usage, levels = c("low", "medium", "high"))
```

```{r}
mari_sub
```

```{r}
ggplot(mari_sub, aes(x = factor(usage), y = IND235, fill = factor(usage))) + 
  geom_boxplot() +
  labs(title = "Distribution of Income", x = "Marijuana Usage", y = "Monthly Family Income", fill = "Marijuana Usage") + 
  scale_fill_brewer(palette="Dark2")
```

For description of data.
```{r}
(table(mari_sub$usage))
(table(pop$DUQ200))
```

```{r}
hist(mari_sub$IND235)
```


Do quitters tend to have higher incomes? Expecting yes. (Not included in report)
```{r}
mari_sub$days_since_smoking <- ifelse(mari_sub$DUQ215U == 1, pop$DUQ215Q, 
              ifelse(mari_sub$DUQ215U == 2, pop$DUQ215Q * 7,
              ifelse(mari_sub$DUQ215U == 3, pop$DUQ215Q * 30, 
                     pop$DUQ215Q * 365)))
hist(log(mari_sub$days_since_smoking))
```

```{r}
lm = lm(IND235 ~ log(days_since_smoking + 1), data = mari_sub)
summary(lm)
```
^ Not significant. Doesn't work with a linear model (no transformations on x) either. 

Working with survey design:
For first graph (smokers vs income)
```{r}
des <- svydesign(ids =  ~SEQN,
                 strata = ~DUQ200,
                 data = pop)
```

```{r}
svymean(~IND235, subset(des, subset = DUQ200 == 1))
svymean(~IND235, subset(des, subset = DUQ200 == 2))
confint(svymean(~IND235, subset(des, subset = DUQ200 == 1)))
confint(svymean(~IND235, subset(des, subset = DUQ200 == 2)))
```


For second graph (frequency vs income)
```{r}
des <- svydesign(ids =  ~SEQN,
                 strata = ~usage,
                 data = mari_sub)
```

```{r}
model.frame(des)
```


```{r}
svymean(~IND235, subset(des, subset = usage == 'low'))
svymean(~IND235, subset(des, subset = usage == 'medium'))
svymean(~IND235, subset(des, subset = usage == 'high'))
confint(svymean(~IND235, subset(des, subset = usage == 'low')))
confint(svymean(~IND235, subset(des, subset = usage == 'medium')))
confint(svymean(~IND235, subset(des, subset = usage == 'high')))
```

Getting table of variables used in analysis:

```{r}
table(df$DUQ200, useNA = 'always')
table(df$DUQ217, useNA = 'always')
table(df$INQ020, useNA = 'always')
table(df$IND235, useNA = 'always')

prop.table(table(df$DUQ200, useNA = 'always'))
prop.table(table(df$DUQ217, useNA = 'always'))
prop.table(table(df$INQ020, useNA = 'always'))
prop.table(table(df$IND235, useNA = 'always'))
```

